\cvsection{\href{https://github.com/Braden1996?tab=repositories}{Side Projects}}

\begin{cvopensource}
  \cvproject
    {\href{https://github.com/Braden1996/Icarus}{Icarus}}
    {
      a tiling windows manager, featuring gaps, created for MacOS. Implemented using a \textit{binary space partitioning tree} plus custom algorithms for efficient querying and layout computations. Can be attached to any graphical interface, such as the DOM of a web-page.
    }

  \cvproject
    {\href{https://github.com/Braden1996/BradensPoon}{BradensPoon}}
    {
      enables MacOS users to create new Terminal windows by dragging a selection box over the screen. Published \href{https://blog.theodo.fr/2018/03/making-runtime-funtime-hammerspoon/}{a technical article} detailing how it was built, which got over 1,000 upvotes \href{https://www.reddit.com/r/unixporn/comments/82opm5/ocmacos_drawing_iterm_windows/}{on Reddit}.
    }

  \cvproject
    {TWERK}
    {
      an administrative addon for Garry's Mod, featuring: a sophisticated GUI; user groups with permissions; powerful user commands; as well as rich plugin and theme systems.
    }

  \cvproject
    {VULK}
    {
      bodybuilding workout tracking app, built with React Native, centred around progressive overload and improvement-focussed analytics. Heavy focus on user-interface; with native-like gestures, animations etc.
    }

  \cvproject
    {\href{https://github.com/Braden1996/Audio-Synthesiser}{Audio Synthesiser}}
    {
      built with MATLAB implementing several \textit{ASP} algorithms (including \textit{spectrogram editing}, \textit{phase vocoder}, \textit{ADSR volume shaping}, \textit{wah-wah}, \textit{flanger} etc). Intuitive GUI and effect pipeline enable some powerful creations.
    }
\end{cvopensource}
